Implementation of a minimum branch-decomposition and branch-width algorithm for planar graphs.

### 2024-09-02 paper/images/k4/cd.tex
Add drawings

\begin{tikzpicture}
	\begin{scope}[xshift=6cm, yshift=0cm]
		\node[circle, draw, color=black, fill=white] (b1) at (3, 4) {\{1,3\}};
		\node[circle, draw, color=black, fill=white] (b3) at (-0.5, 3) {\{1,4\}};
		\node[circle, draw, color=black, fill=white] (10) at (1.5, 4) {10};
		\node[circle, draw, color=black, fill=white] (9) at (1, 3) {9};
		\node[circle, draw, color=black, fill=white] (8) at (1.5, 2) {8};
		\node[circle, draw, color=black, fill=white] (7) at (1, 1) {7};
		\node[circle, draw, color=black, fill=white] (b2) at (3, 2) {\{2,4\}};
		\node[circle, draw, color=black, fill=white] (b4) at (-0.5, 1) {\{2,3\}};
		\node[circle, draw, color=black, fill=white] (b5) at (1, -0.5) {\{3,4\}};
		\node[circle, draw, color=black, fill=white] (b6) at (1.5, 5.5) {\{1,2\}};

@@

		\node (G) at (3, -0.25) {\{2,3,4\}};

>>>>

\begin{tikzpicture}
	\begin{scope}[xshift=6cm, yshift=0cm]
		\node[circle, draw, color=black, fill=white] (b1) at (3, 4) {2};
		\node[circle, draw, color=black, fill=white] (b3) at (-0.5, 3) {3};
		\node[circle, draw, color=black, fill=white] (10) at (1.5, 4) {};
		\node[circle, draw, color=black, fill=white] (9) at (1, 3) {};
		\node[circle, draw, color=black, fill=white] (8) at (1.5, 2) {};
		\node[circle, draw, color=black, fill=white] (7) at (1, 1) {};
		\node[circle, draw, color=black, fill=white] (b2) at (3, 2) {4};
		\node[circle, draw, color=black, fill=white] (b4) at (-0.5, 1) {5};
		\node[circle, draw, color=black, fill=white] (b5) at (1, -0.5) {6};
		\node[circle, draw, color=black, fill=white] (b6) at (1.5, 5.5) {1};

@@

		\node (G) at (3, -0.25) {\{2,3,4,6,7,9\}};

### 2024-09-02 paper/images/k4/quiet/k5/11.tex
Add drawings

		% Draw the edges between nodes with labels
		\draw[dashed, line width=3] (5) -- node[below left] {1} (6);
		\draw[dashed] (5) -- node[above right] {2} (4);
		\draw[dashed] (4) -- node[above left] {3} (6);
		\draw[dashed] (3) -- node[below] {4} (6);
		\draw[draw, line width=1] (3) -- node[right] {5} (2);
		\draw[dashed] (6) -- node[left] {6} (2);
		\draw[dashed] (2) -- node[below left] {7} (5);
		\draw[draw, line width=1] (1) -- node[below right] {8} (2);
		\draw[dashed] (1) -- node[above] {9} (5);
		\draw[draw, line width=1] (1) -- node[above left] {10} (4);
		\draw[draw, line width=1] (1) -- node[below right] {11} (3);
		\draw[draw, line width=1] (4) -- node[above right] {12} (3);
	\end{scope}
\end{tikzpicture}

>>>>

		% Draw the edges between nodes with labels
		\draw[draw, line width=1] (5) -- node[below left] {1} (6);
		\draw[draw, line width=1] (5) -- node[above right] {2} (4);
		\draw[draw, line width=1] (4) -- node[above left] {3} (6);
		\draw[dashed] (3) -- node[below] {4} (6);
		\draw[dashed] (3) -- node[right] {5} (2);
		\draw[draw, line width=1] (6) -- node[left] {6} (2);
		\draw[draw, line width=1] (2) -- node[below left] {7} (5);
		\draw[dashed] (1) -- node[below right] {8} (2);
		\draw[dashed] (1) -- node[above] {9} (5);
		\draw[dashed] (1) -- node[above left] {10} (4);
		\draw[dashed, line width=3] (1) -- node[below right] {11} (3);
		\draw[dashed] (4) -- node[above right] {12} (3);
	\end{scope}
\end{tikzpicture}

### 2024-09-02 paper/images/k4/quiet/k5/12.tex
Add drawings

		% Draw the edges between nodes with labels
		\draw[draw, line width=1] (5) -- node[below left] {1} (6);
		\draw[draw, line width=1] (5) -- node[above right] {2} (4);
		\draw[draw, line width=1] (4) -- node[above left] {3} (6);
		\draw[dashed] (3) -- node[below] {4} (6);
		\draw[dashed] (3) -- node[right] {5} (2);
		\draw[draw, line width=1] (6) -- node[left] {6} (2);
		\draw[draw, line width=1] (2) -- node[below left] {7} (5);
		\draw[dashed] (1) -- node[below right] {8} (2);
		\draw[dashed] (1) -- node[above] {9} (5);
		\draw[dashed] (1) -- node[above left] {10} (4);
		\draw[dashed, line width=3] (1) -- node[below right] {11} (3);
		\draw[dashed] (4) -- node[above right] {12} (3);
	\end{scope}
\end{tikzpicture}

>>>>

		% Draw the edges between nodes with labels
		\draw[draw, line width=1] (5) -- node[below left] {1} (6);
		\draw[dashed] (5) -- node[above right] {2} (4);
		\draw[dashed] (4) -- node[above left] {3} (6);
		\draw[dashed] (3) -- node[below] {4} (6);
		\draw[dashed] (3) -- node[right] {5} (2);
		\draw[draw, line width=1] (6) -- node[left] {6} (2);
		\draw[draw, line width=1] (2) -- node[below left] {7} (5);
		\draw[draw, line width=1] (1) -- node[below right] {8} (2);
		\draw[draw, line width=1] (1) -- node[above] {9} (5);
		\draw[dashed] (1) -- node[above left] {10} (4);
		\draw[dashed] (1) -- node[below right] {11} (3);
		\draw[dashed, line width=3] (4) -- node[above right] {12} (3);
	\end{scope}
\end{tikzpicture}

### 2024-09-02 paper/images/k4/zcontract2.tex
Add drawings

\begin{tikzpicture}
	\node (G) at (2, 1) {Contract $(5,6)$};
	% Define the nodes with specific positions
	\begin{scope}[xshift=0cm, yshift=0cm, scale=0.6]
		\node[circle, draw] (1) at (8, -0) {1};
		\node[circle, draw] (2) at (3, -8) {2};
		\node[circle, draw] (3) at (4, -3.5) {3};
		\node[circle, draw] (4) at (3, -1.5) {4};
		\node[circle, draw] (7) at (-2, -0) {7};

		% Draw the edges between nodes with labels
		\draw[draw] (7) to[bend left=5] node[above right] {2} (4);
		\draw[draw] (4) to[bend left=5] node[above left] {3} (7);
		\draw[draw] (3) -- node[below] {4} (7);
		\draw[draw] (3) -- node[right] {5} (2);
		\draw[draw] (7) to[bend left=5] node[left] {6} (2);
		\draw[draw] (2) to[bend left=5] node[below left] {7} (7);
		\draw[draw] (1) -- node[below right] {8} (2);
		\draw[draw] (1) -- node[above] {9} (7);
		\draw[draw] (1) -- node[above left] {10} (4);
		\draw[draw] (1) -- node[below right] {11} (3);
		\draw[draw] (4) -- node[above right] {12} (3);
	\end{scope}
\end{tikzpicture}

>>>>

\begin{tikzpicture}
	\node (G) at (2, 1) {Contract $(7,4)$};
	% Define the nodes with specific positions
	\begin{scope}[xshift=0cm, yshift=0cm, scale=0.6]
		\node[circle, draw] (1) at (8, -0) {1};
		\node[circle, draw] (2) at (3, -8) {2};
		\node[circle, draw] (3) at (4, -3.5) {3};
		\node[circle, draw] (8) at (-2, -0) {8};

		% Draw the edges between nodes with labels
		\draw[draw] (3) to[bend left=5] node[below] {4} (8);
		\draw[draw] (3) -- node[right] {5} (2);
		\draw[draw] (8) to[bend left=5] node[left] {6} (2);
		\draw[draw] (2) to[bend left=5] node[below left] {7} (8);
		\draw[draw] (1) -- node[below right] {8} (2);
		\draw[draw] (1) to[bend right=5] node[above] {9} (8);
		\draw[draw] (1) to[bend left=5] node[above left] {10} (8);
		\draw[draw] (1) -- node[below right] {11} (3);
		\draw[draw] (8) to[bend left=5] node[above right] {12} (3);
	\end{scope}
\end{tikzpicture}

### 2024-09-02 paper/images/k4/zcontract3.tex
Add drawings

\begin{tikzpicture}
	\node (G) at (2, 1) {Contract $(7,4)$};
	% Define the nodes with specific positions
	\begin{scope}[xshift=0cm, yshift=0cm, scale=0.6]
		\node[circle, draw] (1) at (8, -0) {1};
		\node[circle, draw] (2) at (3, -8) {2};
		\node[circle, draw] (3) at (4, -3.5) {3};
		\node[circle, draw] (8) at (-2, -0) {8};

		% Draw the edges between nodes with labels
		\draw[draw] (3) to[bend left=5] node[below] {4} (8);
		\draw[draw] (3) -- node[right] {5} (2);
		\draw[draw] (8) to[bend left=5] node[left] {6} (2);
		\draw[draw] (2) to[bend left=5] node[below left] {7} (8);
		\draw[draw] (1) -- node[below right] {8} (2);
		\draw[draw] (1) to[bend right=5] node[above] {9} (8);
		\draw[draw] (1) to[bend left=5] node[above left] {10} (8);
		\draw[draw] (1) -- node[below right] {11} (3);
		\draw[draw] (8) to[bend left=5] node[above right] {12} (3);
	\end{scope}
\end{tikzpicture}

>>>>

\begin{tikzpicture}
	\node (G) at (2, 1) {Contract $(8,3)$};
	% Define the nodes with specific positions
	\begin{scope}[xshift=0cm, yshift=0cm, scale=0.6]
		\node[circle, draw] (1) at (8, -0) {1};
		\node[circle, draw] (2) at (3, -8) {2};
		\node[circle, draw] (9) at (-2, -0) {9};

		% Draw the edges between nodes with labels
		\draw[draw] (9) -- node[right] {5} (2);
		\draw[draw] (9) to[bend left=5] node[left] {6} (2);
		\draw[draw] (2) to[bend left=5] node[below left] {7} (9);
		\draw[draw] (1) -- node[below right] {8} (2);
		\draw[draw] (1) to[bend right=5] node[above] {9} (9);
		\draw[draw] (1) to[bend left=5] node[above left] {10} (9);
		\draw[draw] (1) -- node[below right] {11} (9);
	\end{scope}
\end{tikzpicture}

### 2024-09-02 paper/main.tex
Add drawings

@@

@@

@@

@@

@@

@@

@@

@@

@@

			Solving problem \ref{problem:dual}

>>>>

	The tetrahedral graph is a simple connected planar graph with 4 vertices and 6 edges. It is also know as the complete graph on 4 vertices $K_4$. The tetrahedral graph is used as a running example.

	\begin{figure}[H]
		\centering
		% \includegraphics[width=\textwidth/2]{./images/k4/gm.png}
		\input{./images/k4/g.tex}
		\caption{The tetrahedral graph}
		\label{fig:tetrahedral}
	\end{figure}

@@

	\begin{figure}[H]
		\centering
		\input{images/k4/bd.tex}
		\caption{Minimum Branch Decomposition of the Tetrahedral Graph with a branch width of 3.}
		\label{fig:bd}
	\end{figure}

@@

		\begin{figure}[H]
			\centering
			\input{./images/k4/gmedial.tex}
			\caption{The Tetrahedral Graph (in black) and Medial graph of the Tetrahedral Graph (in blue)}
			\label{fig:gmedial}
		\end{figure}

@@

		\begin{figure}[H]
			\centering
			\input{images/k4/bd.tex}
			\input{images/k4/cd.tex}
			\caption{Minimum Branch Decomposition (left) of the Tetrahedral Graph and a Minimum Carving Decomposition (right) of the Medial Graph.}
			\label{fig:m}
		\end{figure}

@@

		\begin{figure}[H]
			\centering
			\input{./images/k4/m.tex}
			\input{./images/k4/zcontract1.tex}
			\input{./images/k4/zcontract2.tex}
			\input{./images/k4/zcontract3.tex}
			\input{images/k4/cd.tex}
			\caption{A series of contractions of the medial graph of the Tetrahedral Graph, with nonincreasing carving width. All graphs have a carving width of $6$. First contracting $(5,6)$ into $7$, then $(7,4)$ into $8$, and finally $(8,3)$ into $9$. Then assembling the series of contractions into a minimum carving decomposition by introducing vertex $10$.}
			\label{fig:m}
		\end{figure}

@@

			\begin{figure}[H]
				\centering
				\input{./images/k4/m.tex}
				\input{./images/k4/zcontract1.tex}
				\caption{A contraction of the medial graph of the Tetrahedral Graph given $(5,6)$ producing a new vertex $7$.}
				\label{fig:m}
			\end{figure}

@@

			For the medial of the tetrahedral graph, the linear search gives for \mintinline{py}{rat_wins} for $k=0,1,2,3,4,5,6,7$ gives $True, True, True, True, True, True, True, False$, therefore the carving width of the medial of the tetrahedral graph is $6$.

@@

			Solving problem \ref{problem:dual}.

			\begin{figure}[H]
				\centering
				\input{./images/k4/dual.tex}
				\caption{The medial graph of the Tetrahedral Graph and its dual. Vertex 5 is the vertex for the outerface and therefore visually repeated.}
				\label{fig:m}
			\end{figure}

		\subsection{Does the rat win?}

@@

			\begin{figure}[H]
				\centering
				\input{./images/k4/quiet/k5/1.tex}
				\input{./images/k4/quiet/k5/2.tex}
				\input{./images/k4/quiet/k5/3.tex}
				\input{./images/k4/quiet/k5/4.tex}
				\input{./images/k4/quiet/k5/5.tex}
				\input{./images/k4/quiet/k5/6.tex}
				\input{./images/k4/quiet/k5/7.tex}
				\input{./images/k4/quiet/k5/8.tex}
				\input{./images/k4/quiet/k5/9.tex}
				\input{./images/k4/quiet/k5/10.tex}
				\input{./images/k4/quiet/k5/11.tex}
				\input{./images/k4/quiet/k5/12.tex}
				\caption{The medial of the Tetrahedral Graph and the quiet components for noise level $k=5$, given the rat-catcher is on edge $1,...,12$.}
				\label{fig:quiet}
			\end{figure}

@@

			\begin{figure}[H]
				\centering
				\input{images/k4/quiet/quiet-k4-k5-e9.tex}
				\caption{The quiet component for edge $9$ with noise level $k=5$. The quiet edges are in solid and the noisy edges are dashed. Vertex 5 is the vertex for the outerface and therefore visually repeated.}
				\label{fig:quiet}
			\end{figure}
